Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-06-03 paper.tex
closing issues: Closes #11
closing issues: Closes #30
Revising references and including some new in KBS

At this stage, a Feature Selection (FS) process has been carried out, since it is an effective dimensionality reduction technique and an essential preprocessing method to discard less relevant or non-useful features \cite{Krishnapuram2004}.

@@

Thus, in our experiments, the best value of $k$ in the $k$-nearest neighbour was empirically found at $k=3$. % What???? - JJ
For SVM, the widely used Radial Basis Function (RBF) kernel is selected. As reported in several studies, RBF kernel has a reliable performance and can analyse higher dimensional data \cite{yu2004ec,chao2015construction,huang2006ga}. Two important
parameters should be tuned in SVM: the Cost $(C)$ and Gamma $(\gamma)$ of
the RBF kernel. We apply grid search which is the most common approach
to find $C$ and $\gamma$. The best performance of SVM was found at
$C=200$ and $\gamma = 0.01$. For MLP, we apply it with one
hidden layer since it was proven in the literature that an MLP with
one hidden layer can approximate any continuous or discontinuous
function \cite{hornik1989multilayer,mirjalili2014let}. However, there
is no rule of thumb for selecting the best number of neurons in the
hidden layer. One suggested method that is followed in this work is to
set the number of neurons in the hidden layer to $2 \times I + 1$
where $I$ is the number of inputs in the dataset
\cite{wdaa2008differential,mirjalili2014let,mirjalili2015effective}.

@@

As future work, it would be interesting to compare the obtained
forecasting results with those yielded by other soft-computing
methods, such as genetic programming or fuzzy logic. 
Moreover, even if the methods have been configured to obtain the best
forecasting results, it would be of interest carrying out some
automatic parameter-tuning procedure by means of optimisation
meta-algorithms \cite{Cheng2006_tunningSVM,Lessmann2011_tunningDM},  
% Antonio - add an ESWA reference to this. :D
% Antonio - I have done it.
for instance.

@@

This work has been supported in part by projects PreTEL (PRM Consultores - Trevenque S.L.), TIN2014-56494-C4-3-P and TEC2015-68752 (Spanish Ministry of Economy and Competitiveness), PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci{\'o}n), and PROY-PP2015-06 (Plan Propio 2015, funded by the University of Granada, Spain).

>>>>

At this stage, a Feature Selection (FS) process has been carried out, since it is an effective dimensionality reduction technique and an essential preprocessing method to discard less relevant or non-useful features \cite{Krishnapuram2004,Chen2011_FS_PTS}.

@@

Thus, in our experiments, the best value of $k$ in the $k$-nearest neighbour was empirically found at $k=3$. % What???? - JJ
For SVM, the widely used Radial Basis Function (RBF) kernel is selected. As reported in several studies, RBF kernel has a reliable performance and can analyse higher dimensional data \cite{yu2004ec,chao2015construction}. Two important parameters should be tuned in SVM: the Cost $(C)$ and Gamma $(\gamma)$ of the RBF kernel. We apply grid search which is the most common approach
to find $C$ and $\gamma$. The best performance of SVM was found at
$C=200$ and $\gamma = 0.01$. For MLP, we apply it with one
hidden layer since it was proven in the literature that an MLP with
one hidden layer can approximate any continuous or discontinuous
function \cite{hornik1989multilayer,mirjalili2014let}. However, there
is no rule of thumb for selecting the best number of neurons in the
hidden layer. One suggested method that is followed in this work is to
set the number of neurons in the hidden layer to $2 \times I + 1$
where $I$ is the number of inputs in the dataset
\cite{wdaa2008differential,mirjalili2014let,mirjalili2015effective}.

@@

As future work, it would be interesting to compare the obtained
forecasting results with those yielded by other soft-computing
methods, such as genetic programming or fuzzy logic. 
Moreover, even if the methods have been configured to obtain the best
forecasting results, it would be of interest carrying out some
automatic parameter-tuning procedure by means of optimisation
meta-algorithms \cite{huang2006ga,Mookiah2013_EA_Tuning,Shen2016_FFly_Tuning},  
% Antonio - changed to include KBS references
for instance.

@@

This work has been supported in part by projects PreTEL (PRM Consultores - Trevenque S.L.), TIN2014-56494-C4-3-P and TEC2015-68752 (Spanish Ministry of Economy and Competitiveness and FEDER), PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci{\'o}n), and PROY-PP2015-06 (Plan Propio 2015, funded by the University of Granada, Spain).
